---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gilmoregirls

<!-- badges: start -->
<!-- badges: end -->

The goal of gilmoregirls is to provide the complete script transcription of the Gilmore Girls (*work in progress*) and information about the episodes of the TV Show. 


## Installation

You can install the development version of gilmoregirls from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lgiselebock/gilmoregirls")
```

## Example

The `gilmoregirls` package comes with one dataset, that contains the information about all the episodes in the show.

```{r example}
library(gilmoregirls)

dplyr::glimpse(gilmoregirls_info)
```

### Audience (in millions) in the USA

```{r}


gilmoregirls_info |> 
  dplyr::mutate(season = as.factor(season)) |> 
  ggplot2::ggplot() +
  ggplot2::aes(
    x = index,
    y = us_views_millions,
    fill = season,
    width = 0.5
  ) +
  ggplot2::geom_col() +
  ggplot2::labs(
    x = "Episodes",
    y = "Audience (millions) in the USA",
    fill = "Season"
  ) +
  ggplot2::scale_x_continuous(breaks = seq(0, 153, 20)) +
  ggplot2::scale_y_continuous(
    limits = c(0, 8), 
    breaks = seq(0, 8, 2)
  ) +
  ggplot2::scale_fill_manual(
    values = c(
      "#d4b9a9",
      "#5271ff",
      "#52c5c7",
      "#c131e8",
      "#fc9b5e",
      "#ffdd49",
      "#cd570f"
    )
  ) +
  ggplot2::theme_minimal() +
  ggplot2::theme(
    panel.grid.major.x = ggplot2::element_blank(),
    panel.grid.minor = ggplot2::element_blank(),
    legend.position = c(1.06, 1.06),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    plot.margin = ggplot2::unit(c(1, 1, 1, 1), "cm"),
    text = ggplot2::element_text(size = 10)
  )

```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
